Verifying Demonstrations

### 2018-08-28 paper/protocol.tex
Minor clarification for CA footnote in protocol

Several entities are involved in our protocol.
First, \iac{CA} is responsible for certifying a one-to-one mapping between a person's identity and a cryptographic key.
The \ac{CA} is only involved in the setup phase.
Second, a protester is an individual who wants to participate in a given protest.
A protester can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and forward it to others.
\item A \emph{participant} is attending the protest and asks witnesses to vouch for his presence.
\item A \emph{witness} provides proofs to participants that state the participant was indeed participating and such that the proofs are verifiable by third parties.
\end{enumerate}
In general, there is one organizer and every protester will act alternatively as both participant and witness.

>>>>

Several entities are involved in our protocol.
First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key\footnote{%
  This can be done by a centralized authority, such as a nation state with, 
  \eg, passports; or a decentralized authority, as in the case of 
  proof-of-personhood~\cite{proof-of-personhood}.
}.
The \ac{CA} is only involved in the setup phase.
Second, a protester is an individual who wants to participate in a given protest.
A protester can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and forward it to others.
\item A \emph{participant} is attending the protest and asks witnesses to vouch for his presence.
\item A \emph{witness} provides proofs to participants that state the participant was indeed participating and such that the proofs are verifiable by third parties.
\end{enumerate}
In general, there is one organizer and every protester will act alternatively as both participant and witness.
